Contextual Combinatorial Cascading Bandits

### 2015-12-07 contextual combinatorial cascading bandits.tex
update symbols
update proof details

To state our main theorem, we need some definitions. Let
$$
f_{\wedge}^* = \max_{1 \leq t \leq T} f_{\wedge, t}^{\ast}
$$
denote the best expected reward of all time under the conjunctive objective.
Let $p_{t, A}$ (resp., $p_{\wedge, t, A}$) be the {\em probability of full
	observation of $A$, that is the probability that all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ are observed under the disjunctive objective (resp., conjunctive objective) when under the context of time $t$, that is 
\begin{align*}
&p_{t, A} = \prod_{k=1}^{\abs{A}-1} (1 - \theta_{\ast}^{\top} x_{t, a_k^t}),\\
&p_{\wedge, t, A} = \prod_{k=1}^{\abs{A}-1} (\theta_{\ast}^{\top} x_{t, a_k^t}).
\end{align*}
We also define $p^* = \min_{1 \leq t \leq T} \min_{A \in \cS} ~ p_{t, A}$ to be the minimal probability over all time that an action could have all base arms observed under the disjunctive objective. The following is the main theorem on the regret achieved by our C$^3$-UCB algorithm, for both the disjunctive and conjunctive objectives.
\begin{theorem}
\label{thm:main}
Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and 
$\gamma_k' = 1 - \gamma_k, \gamma'_K \leq \frac{1}{4}f_{\wedge}^{\ast}$.
Let regularization parameter $\lambda$ satisfy $\lambda \geq C_\gamma$, where $C_\gamma = \sum_{k=1}^{K} \gamma_k^2$. Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regrets of our algorithm, C$^3$-UCB for both the conjunctive and disjunctive objectives, satisfy
\begin{align}
R(T) &\le \frac{\sqrt{2}}{p^*} \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))}  \nonumber \\
&\qquad \cdot \left(\sqrt{d\ln(1 + C_\gamma T/(\lambda d)) + 2\ln\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}\right) \nonumber \\
&=O\left(\frac{d}{p^*} \sqrt{TK} \ln T\right),
\end{align}
\begin{align}
R_{\wedge}(T) &\le \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))} \nonumber \\
&\qquad \cdot \left(\sqrt{d\ln(1 + C_\gamma T/(\lambda d)) + 2\ln\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}\right) \nonumber \\
&=O\left(\frac{d}{f_{\wedge}^{\ast}}\sqrt{TK} \ln T\right).
\end{align}
%where
%\begin{align*}
%C_\gamma = \sum_{k=1}^{K} \gamma_k^2 = \sum_{k=1}^{K} (1 - \gamma_k')^2 \in [1, K].
%\end{align*}
\end{theorem}

@@

We first provide a basic property of functions $f$ and $f_{\wedge}$ as defined
in~Eq.\eqref{eq:functionf} and \eqref{eq:functionfstar}.
\begin{lemma}
\label{lem:increasing} 
Suppose $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Then $f(A, w)$ and $f_{\wedge}(A, w)$ are increasing with respect to $w$; that is, if $0 \leq w \leq w' \leq 1$ as column vectors in $\RR^L$, then for any $A \in \prod^{\leq K}$, it holds that
$$
f(A, w) \leq f(A, w'), ~~ f_{\wedge}(A, w) \leq f_{\wedge}(A, w').
$$
\end{lemma}
\begin{proof}
Without the loss of generality, we prove for the case
	of $A = (1, \ldots, m)$, where $1 \leq m \leq K$. 
First, for $1 \leq k \leq m$, we have
\begin{align*}
&\gamma_{k} - \sum_{i=k+1}^m \gamma_i \prod_{j = k + 1}^{i - 1} (1 - w_j') w_i'\\
\geq &~\gamma_k [1 - \sum_{i=k+1}^m \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
\geq &~\gamma_{k} \cdot 0 = 0,
\end{align*}
Then it implies that
\begin{align*}
&\gamma_k w_k + (1 - w_k)\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i'\\
\leq &\gamma_k w_k' + (1 - w_k')\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i'\\
\end{align*}
Therefore, 
\begin{align*}
& f(A; w_1, \dots, w_k, w_{k+1}', \dots, w_m')\\
&=\sum_{i=1}^{k-1} \gamma_i \prod_{j=1}^{i-1}(1 - w_j) w_i + \prod_{j=1}^{k-1}(1 - w_j) \\
&\qquad \cdot [\gamma_k w_k + (1 - w_k)\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
&\leq \sum_{i=1}^{k-1} \gamma_i \prod_{j=1}^{i-1}(1 - w_j) w_i + \prod_{j=1}^{k-1}(1 - w_j) \\
&\qquad \cdot [\gamma_k w_k' + (1 - w_k')\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
&=f(A; w_1, \ldots, w_{k-1}, w_{k}', \ldots, w_m').
\end{align*}
By letting $\gamma_k = 1 - \gamma_k'$ and using the relation
	in Eq. \eqref{eq:ConDisRelation}, the increasing property of $f_{\wedge}$ is obtained directly.
\end{proof}

@@

The next lemma provides some properties about a prefix of action $A$
	in the conjunctive case, 
	which leads to the finding of a prefix $B$ of $A$ with similar regret
	and probability of full observation as those of $A$, as given
	in Lemma~\ref{lem:prefixexists}.
\begin{lemma}
\label{lem:prefixRelation}
Suppose 
% $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and 
$0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Let $A = (a_1, ..., a_{\abs{A}})$. 
% For the conjunctive case, it holds that
% $$
% p_A \geq 1 - \frac{f(A, w)}{\gamma_{\abs{A}}}.
% $$
Let $B_k = (a_1, ..., a_k), k \leq \abs{A}$ be a prefix of $A$. Then for the problem with conjunctive objective and $k < \abs{A}$, we have the following properties:
\wei{$p_{\wedge, A}$ is not defined before. Only $p_{\wedge, t, A}$ is defined.
	I guess you are using $w$ vector to be the mean vectors for $A$. Please define
	this clearly.}
\begin{itemize}
\item[(1)] $f_{\wedge}(A, w) \leq \gamma_{\abs{A}}' + (1 - \gamma_{\abs{A}}') p_{\wedge, A}$;
\item[(2)] $f_{\wedge}(B_{k+1}, w) \leq f_{\wedge}(B_k, w)$;
\item[(3)] $p_{\wedge, B_{k+1}} \leq p_{\wedge, B_k}$;
\item[(4)] $f_{\wedge}(B_k, w) \leq \gamma_{k+1}' + (1 - \gamma_{k+1}') p_{B_{k+1}}$.
\end{itemize}
\end{lemma}

@@

\begin{lemma} \label{lem:prefixexists}
Suppose $0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Let $A = (a_1, ..., a_{\abs{A}})$. For the time $t$ and the conjunctive objective, there exists a prefix $B$ of $A$ such that 
$$
p_{\wedge, B} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{B}}', \qquad R_{\wedge}(t, B) \geq \frac{1}{2} R_{\wedge}(t, A).
$$ 
\end{lemma}
\begin{proof}
If $f_{\wedge}(A, w) \geq \frac{1}{2} f_{\wedge, t}^{\ast}$, then by Lemma \ref{lem:prefixRelation},
$$
p_{\wedge, A} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{A}}'.
$$

Suppose $f_{\wedge}(A, w) \leq \frac{1}{2} f_{\wedge, t}^{\ast}$. Let
$$
x_k = f_{\wedge}(B_k,w), ~~ y_k = \gamma_k' + (1 - \gamma_k')p_{\wedge, B_k}, ~~I_k = [x_k, y_k]
$$
Then by Lemma \ref{lem:prefixRelation}, we have $x_k \leq y_k$, $x_{k+1} \leq x_k \leq y_{k+1}$. Therefore, $I_k$ is indeed an interval and $I_k \cap I_{k+1} \neq \emptyset$. Also, $x_{\abs{A}} = f_{\wedge}(A, w)$ and $y_1 = 1$. Thus
$$
[f_{\wedge}(A,w), 1] = \bigcup_{k=1}^{\abs{A}} I_k.
$$
Then there exists a $k$ such that $\frac{1}{2}f_{\wedge, t}^{\ast} \in I_k$:
$$
f_{\wedge}(B_k,w) \leq \frac{1}{2}f_{\wedge, t}^{\ast} \leq \gamma_k' + (1 - \gamma_k')p_{\wedge, B_k}
$$
Therefore, the results are derived.
\end{proof}

\begin{lemma}
Let $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $\gamma_k' = 1 - \gamma_k$. Suppose the equation (\ref{eq:estimateTheta}) holds for all time $t$. Then
$$
E[R(t, \bA_t)|\cH_t] \leq \frac{1}{p^*} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}
$$
If we have
% $$
% \gamma_K \geq (1+\frac{1}{n_0})f^{\ast}, \qquad 
% $$
$$
\gamma_K' \le \frac{1}{4} f_{\wedge}^{\ast},
$$
then
\begin{align*}
% &E[\Delta_{t, \bA_t}|\cH_t] \leq (n_0+1) \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}},\\
&E[R_{\wedge}(t, \bA_t)|\cH_t] \leq \frac{8}{f_{\wedge}^{\ast}} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}},
\end{align*}
where $f^{\ast} = \max_{t} f_t^{\ast}, f_{\wedge}^{\ast} = \max_{t} f_{\wedge, t}^{\ast}$.
\end{lemma}
\begin{proof}
For the disjunctive case,  $p_{\bA_t} \geq p^*$ by definition and the result can be derived directly.
% $p_{\bA_t} \geq \frac{1}{n_0 + 1}$ by lemma \ref{lem:prefixRelation} and the result can be derived directly.

For the conjunctive case, there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\wedge, \bB_t} \geq \frac{1}{4}f_{\wedge, t}^*$ and $R_{\wedge}(t, \bB_t) \geq \frac{1}{2} R_{\wedge}(t, \bA_t)$. Then we have
$$
\EE_t[R_{\wedge}(t, \bA_t)] \leq \frac{8}{f_{\wedge, t}^*} \EE_t[R_{\wedge}(t, \bB_t) \bOne\{R_{\wedge}(t, \bB_t) > 0, \bO_t \geq \abs{\bB_t}\}
$$
Because 
$$
f_{\wedge}(A_t^*, \theta_*^{\top}X_t) \leq f_{\wedge}(A_t^*,\bU_t) \leq f_{\wedge}(\bA_t,\bU_t) \leq f_{\wedge}(\bB_t,\bU_t)
$$
by Lemma \ref{lem:increasing} and
$$
f_{\wedge}(\bB_t,\bU_t) \leq f_{\wedge}(\bB_t, \theta_*^{\top}x_t) + \sum_{k=1}^{\abs{\bB_t}}\gamma_k\beta_{t-1}(\delta)\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
$$
by Lemma \ref{lem:estimateTech}, we have
$$
R_{\wedge}(t, \bB_t) \leq \sum_{k=1}^{\abs{\bB_t}}\beta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
$$
\end{proof}

@@

\begin{lemma}
If $\lambda \geq C_\gamma$, then
$$
\sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2\ln(\frac{\det(\bV_t)}{\det(\lambda I)}).
$$
\end{lemma}
\begin{proof}
\begin{align*}
&\det(\bV_t) = \det(\bV_{t-1} + \sum_{k=1}^{\bO_t} (\gamma_k X_{t,\ba_k^{t}})(\gamma_k X_{t, \ba_k^{t}}^{\top}))\\
&=\det(\bV_{t-1})\\
&~~~\cdot \det(I + \sum_{k=1}^{\bO_t} \gamma_k \bV_{t-1}^{-1/2}x_{t,\ba_{k}^{t}} (\gamma_k \bV_{t-1}^{-1/2}x_{t,\ba_{k}^{t}})^{\top})\\
&\geq \det(\bV_{t-1}) (1 + \sum_{k=1}^{\bO_t} \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2)\\
&\geq \det(\lambda I)\prod_{s=1}^{t}(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2)
\end{align*}
Because
$$
\norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \leq \norm{\gamma_k x_{s,\ba_k^s}}_2^2/\lambda_{\min}(\bV_{s-1}) \leq \gamma_k^2 /\lambda,
$$
we have 
$$
\sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \leq \frac{1}{\lambda} \sum_{k=1}^{K} \gamma_k^2 = C_\gamma /\lambda \leq 1
$$
Using the fact that $ 2\ln(1+u) \geq u$ for any $u \in [0,1]$, we get
\begin{align*}
&\sum_{s=1}^t \sum_{k=1}^{\bO_s}\norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \\
&\leq 2\sum_{s=1}^t\ln(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2)\\
&\leq 2(\ln(\det(\bV_t)) - \ln(\det(\lambda I))) \\
&= 2 \ln(\frac{\det(\bV_t)}{\det(\lambda I)})
\end{align*}
\end{proof}

>>>>

To state our main theorem, we need some definitions. Let
$$
f_{\wedge}^* = \min_{1 \leq t \leq T} f_{\wedge, t}^{\ast}
$$
denote the best expected reward of all time under the conjunctive objective.
Let $p_{t, A}$ (resp., $p_{\wedge, t, A}$) be the {\em probability of full
	observation of $A$}, that is the probability that all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ are observed under the disjunctive objective (resp., conjunctive objective) when under the context of time $t$, that is 
\begin{align*}
&p_{t, A} = \prod_{k=1}^{\abs{A}-1} (1 - \theta_{\ast}^{\top} x_{t, a_k^t}),\\
&p_{\wedge, t, A} = \prod_{k=1}^{\abs{A}-1} (\theta_{\ast}^{\top} x_{t, a_k^t}).
\end{align*}
We also define $p^* = \min_{1 \leq t \leq T} \min_{A \in \cS} ~ p_{t, A}$ to be the minimal probability over all time that an action could have all base arms observed under the disjunctive objective. The following is the main theorem on the regret achieved by our C$^3$-UCB algorithm, for both the disjunctive and conjunctive objectives.
\begin{theorem}
\label{thm:main}
Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and 
$\gamma_k' = 1 - \gamma_k, \gamma'_K \leq \frac{1}{4}f_{\wedge}^{\ast}$.
Let regularization parameter $\lambda$ satisfy $\lambda \geq C_\gamma$, where $C_\gamma = \sum_{k=1}^{K} \gamma_k^2$. Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regrets of our algorithm, C$^3$-UCB for both the conjunctive and disjunctive objectives, satisfy
\begin{align}
R(T) &\le \frac{\sqrt{2}}{p^*} \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))}  \nonumber \\
&\qquad \cdot \left(\sqrt{d\ln(1 + C_\gamma T/(\lambda d)) + 2\ln\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}\right) \nonumber \\
&=O\left(\frac{d}{p^*} \sqrt{TK} \ln T\right),
\end{align}
\begin{align}
R_{\wedge}(T) &\le \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))} \nonumber \\
&\qquad \cdot \left(\sqrt{d\ln(1 + C_\gamma T/(\lambda d)) + 2\ln\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}\right) \nonumber \\
&=O\left(\frac{d}{f_{\wedge}^{\ast}}\sqrt{TK} \ln T\right).
\end{align}
%where
%\begin{align*}
%C_\gamma = \sum_{k=1}^{K} \gamma_k^2 = \sum_{k=1}^{K} (1 - \gamma_k')^2 \in [1, K].
%\end{align*}
\end{theorem}

@@

We first provide a basic property of functions $f$ and $f_{\wedge}$ as defined
in~Eq.\eqref{eq:functionf} and \eqref{eq:functionfstar}.
\begin{lemma}
\label{lem:increasing} 
Suppose $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Then $f(A, w)$ and $f_{\wedge}(A, w)$ are increasing with respect to $w$; that is, if $0 \leq w \leq w' \leq 1$ as column vectors in $\RR^L$, then for any $A \in \prod^{\leq K}$, it holds that
$$
f(A, w) \leq f(A, w'), ~~ f_{\wedge}(A, w) \leq f_{\wedge}(A, w').
$$
\end{lemma}
\begin{proof}
Without the loss of generality, we prove for the case
	of $A = (1, \ldots, m)$, where $1 \leq m \leq K$. 
First, for $1 \leq k \leq m$, we have
\begin{align*}
&\gamma_{k} - \sum_{i=k+1}^m \gamma_i \prod_{j = k + 1}^{i - 1} (1 - w_j') w_i'\\
\geq &~\gamma_k [1 - \sum_{i=k+1}^m \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
\geq &~\gamma_{k} \cdot 0 = 0.
\end{align*}
Then it implies that
\begin{align*}
&\gamma_k w_k + (1 - w_k)\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i'\\
\leq &\gamma_k w_k' + (1 - w_k')\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i'.\\
\end{align*}
Therefore, 
\begin{align*}
& f(A; w_1, \dots, w_k, w_{k+1}', \dots, w_m')\\
&=\sum_{i=1}^{k-1} \gamma_i \prod_{j=1}^{i-1}(1 - w_j) w_i + \prod_{j=1}^{k-1}(1 - w_j) \\
&\qquad \cdot [\gamma_k w_k + (1 - w_k)\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
&\leq \sum_{i=1}^{k-1} \gamma_i \prod_{j=1}^{i-1}(1 - w_j) w_i + \prod_{j=1}^{k-1}(1 - w_j) \\
&\qquad \cdot [\gamma_k w_k' + (1 - w_k')\sum_{i=k+1}^m \gamma_i \prod_{j=k+1}^{i-1}(1 - w_j') w_i']\\
&=f(A; w_1, \ldots, w_{k-1}, w_{k}', \ldots, w_m').
\end{align*}
By letting $\gamma_k = 1 - \gamma_k'$ and using the relation
	in Eq. \eqref{eq:ConDisRelation}, the increasing property of $f_{\wedge}$ is obtained directly.
\end{proof}

@@

The next lemma provides some properties about a prefix of action $A$
	in the conjunctive case, 
	which leads to the finding of a prefix $B$ of $A$ with similar regret
	and probability of full observation as those of $A$, as given
	in Lemma~\ref{lem:prefixexists}.
\begin{lemma}
\label{lem:prefixRelation}
Suppose 
% $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and 
$0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Let $A = (a_1, ..., a_{\abs{A}})$. 
% For the conjunctive case, it holds that
% $$
% p_A \geq 1 - \frac{f(A, w)}{\gamma_{\abs{A}}}.
% $$
Let $B_k = (a_1, ..., a_k), k \leq \abs{A}$ be a prefix of $A$. 
\wei{$p_{\wedge, A}$ is not defined before. Only $p_{\wedge, t, A}$ is defined.
	I guess you are using $w$ vector to be the mean vectors for $A$. Please define
	this clearly.}
\shuai{I have modified this part.}
Suppose we have weights $w$. Let $p_{\wedge, A}$ be the {\em probability of full observation of $A$}, that is the probability that all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ are observed under the conjunctive objective:
$$
p_{\wedge, A} = \prod_{k=1}^{\abs{A}-1} w_{a_k}.
$$
Then for the problem with conjunctive objective and $k < \abs{A}$, we have the following properties:
\begin{itemize}
\item[(1)] $f_{\wedge}(A, w) \leq \gamma_{\abs{A}}' + (1 - \gamma_{\abs{A}}') p_{\wedge, A}$;
\item[(2)] $f_{\wedge}(B_{k+1}, w) \leq f_{\wedge}(B_k, w)$;
\item[(3)] $p_{\wedge, B_{k+1}} \leq p_{\wedge, B_k}$;
\item[(4)] $f_{\wedge}(B_k, w) \leq \gamma_{k+1}' + (1 - \gamma_{k+1}') p_{B_{k+1}}$.
\end{itemize}
\end{lemma}

@@

\begin{lemma} \label{lem:prefixexists}
Suppose $0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Let $A = (a_1, ..., a_{\abs{A}})$. For the time $t$ and the conjunctive objective, there exists a prefix $B$ of $A$ such that 
$$
p_{\wedge, t, B} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{B}}', \qquad R_{\wedge}(t, B) \geq \frac{1}{2} R_{\wedge}(t, A).
$$ 
\end{lemma}
\begin{proof}
If $f_{\wedge}(A, w) \geq \frac{1}{2} f_{\wedge, t}^{\ast}$, then by Lemma \ref{lem:prefixRelation},
$$
p_{\wedge, t, A} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{A}}'.
$$

Suppose $f_{\wedge}(A, w) \leq \frac{1}{2} f_{\wedge, t}^{\ast}$. Let
$$
x_k = f_{\wedge}(B_k,w), ~~ y_k = \gamma_k' + (1 - \gamma_k')p_{\wedge, B_k}, ~~I_k = [x_k, y_k]
$$
Then by Lemma \ref{lem:prefixRelation}, we have $x_k \leq y_k$, $x_{k+1} \leq x_k \leq y_{k+1}$. Therefore, $I_k$ is indeed an interval and $I_k \cap I_{k+1} \neq \emptyset$. Also, $x_{\abs{A}} = f_{\wedge}(A, w)$ and $y_1 = 1$. Thus
$$
[f_{\wedge}(A,w), 1] = \bigcup_{k=1}^{\abs{A}} I_k.
$$
Then there exists a $k$ such that $\frac{1}{2}f_{\wedge, t}^{\ast} \in I_k$:
$$
f_{\wedge}(B_k,w) \leq \frac{1}{2}f_{\wedge, t}^{\ast} \leq \gamma_k' + (1 - \gamma_k')p_{\wedge, t, B_k}
$$
Therefore, the results are derived.
\end{proof}

\begin{lemma}
Let $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $\gamma_k' = 1 - \gamma_k$. Suppose the equation (\ref{eq:estimateTheta}) holds for all time $t$. Then
$$
E[R(t, \bA_t)|\cH_t] \leq \frac{1}{p^*} \EE[ \beta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} ].
$$
If we have
% $$
% \gamma_K \geq (1+\frac{1}{n_0})f^{\ast}, \qquad 
% $$
$$
\gamma_K' \le \frac{1}{4} f_{\wedge}^{\ast} = \frac{1}{4} \min_{1 \leq t \leq T} f_{\wedge, t}^{\ast},
$$
then
\begin{align*}
% &E[\Delta_{t, \bA_t}|\cH_t] \leq (n_0+1) \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}},\\
&E[R_{\wedge}(t, \bA_t)|\cH_t] \leq \frac{8}{f_{\wedge}^{\ast}} \EE[\beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}].
\end{align*}
\end{lemma}
\begin{proof}
For the disjunctive case,  $p_{\bA_t} \geq p^*$ by definition and the result can be derived directly.
% $p_{\bA_t} \geq \frac{1}{n_0 + 1}$ by lemma \ref{lem:prefixRelation} and the result can be derived directly.

For the conjunctive case, there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\wedge, \bB_t} \geq \frac{1}{4}f_{\wedge, t}^*$ and $R_{\wedge}(t, \bB_t) \geq \frac{1}{2} R_{\wedge}(t, \bA_t)$. Then we have
$$
\EE_t[R_{\wedge}(t, \bA_t)] \leq \frac{8}{f_{\wedge, t}^*} \EE_t[R_{\wedge}(t, \bB_t) \bOne\{R_{\wedge}(t, \bB_t) > 0, \bO_t \geq \abs{\bB_t}\}]
$$
Because 
$$
f_{\wedge}(A_t^*, \theta_*^{\top}X_t) \leq f_{\wedge}(A_t^*,\bU_t) \leq f_{\wedge}(\bA_t,\bU_t) \leq f_{\wedge}(\bB_t,\bU_t)
$$
by Lemma \ref{lem:increasing} and
$$
f_{\wedge}(\bB_t,\bU_t) \leq f_{\wedge}(\bB_t, \theta_*^{\top}x_t) + \sum_{k=1}^{\abs{\bB_t}}\gamma_k\beta_{t-1}(\delta)\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
$$
by Lemma \ref{lem:estimateTech}, we have
$$
R_{\wedge}(t, \bB_t) \leq \sum_{k=1}^{\abs{\bB_t}}\beta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
$$
Therefore
\begin{align*}
\EE_t[R_{\wedge}(t, \bA_t)] &\leq \EE[\frac{8}{f_{\wedge, t}^*} \bOne\{ \bO_t \geq \abs{\bB_t} \}\sum_{k=1}^{\abs{\bB_t}}\beta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]\\
&\leq \EE[ \frac{8}{f_{\wedge}^*} \sum_{k=1}^{ \bO_t } \beta_{t-1}(\delta) \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} ]
\end{align*}
\end{proof}

@@

\begin{lemma}
If $\lambda \geq C_\gamma$, then
$$
\sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2\ln(\frac{\det(\bV_t)}{\lambda^d}).
$$
\end{lemma}
\begin{proof}
\begin{align*}
&\det(\bV_t) = \det(\bV_{t-1} + \sum_{k=1}^{\bO_t} (\gamma_k X_{t,\ba_k^{t}})(\gamma_k X_{t, \ba_k^{t}}^{\top}))\\
&=\det(\bV_{t-1})\\
&~~~\cdot \det(I + \sum_{k=1}^{\bO_t} \gamma_k \bV_{t-1}^{-1/2}x_{t,\ba_{k}^{t}} (\gamma_k \bV_{t-1}^{-1/2}x_{t,\ba_{k}^{t}})^{\top})\\
&\geq \det(\bV_{t-1}) (1 + \sum_{k=1}^{\bO_t} \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2)\\
&\geq \det(\lambda I)\prod_{s=1}^{t}(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2)
\end{align*}
Because
$$
\norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \leq \norm{\gamma_k x_{s,\ba_k^s}}_2^2/\lambda_{\min}(\bV_{s-1}) \leq \gamma_k^2 /\lambda,
$$
we have 
$$
\sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \leq \frac{1}{\lambda} \sum_{k=1}^{K} \gamma_k^2 = C_\gamma /\lambda \leq 1
$$
Using the fact that $ 2\ln(1+u) \geq u$ for any $u \in [0,1]$, we get
\begin{align*}
&\sum_{s=1}^t \sum_{k=1}^{\bO_s}\norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \\
&\leq 2\sum_{s=1}^t\ln(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2)\\
&\leq 2(\ln(\det(\bV_t)) - \ln(\det(\lambda I))) \\
&= 2 \ln(\frac{\det(\bV_t)}{\det(\lambda I)})
\end{align*}
\end{proof}
